---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# HTSoutliers

<!-- badges: start -->
<!-- badges: end -->

The goal of HTSoutliers is to provide functions to help with the detection
of outliers found in hyrdological time series data.

## Installation

You can install the released version of HTSoutliers from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("HTSoutliers")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("scoutiii/HTSoutliers")
```
## Example

This is a basic example which shows you how to solve a common problem:

Getting data from the GHCND.
You can specify as few or as many different locations as you want, and mix
the type of locations. For example you can get two different states data,
along with some other stations which lie outside of those states, and include
a desired ecoregion.

OUTLIER VARIABLES:
    SNWD
    WESD
    PRCP
    TMIN
    TMAX

```{r example}
library(HTSoutliers)

# UT <- get_weather_data("UT", progress = FALSE)
# head(data)
# UT_Flagged <- create_flagged_dataset(UT)

```

